Shift-sensitive Power Transformations for Transforming Data to Normality

### 2023-03-30 manuscript/manuscript.Rmd
Compute right-sided outliers
Added section on goodness of fit.

To be added.

@@

```{r optimal_weighting_function_all_criteria_box_cox, warning=FALSE, message=FALSE, fig.cap=cap}
cap <- paste0(
  "Things."
)
# This finds lambda values at the optimised weighting parameter settings.
data <- .get_transformation_parameters_two_sided(manuscript_dir = manuscript_dir)

@@

```{r optimal_weighting_function_all_criteria_yeo_johnson, warning=FALSE, message=FALSE, fig.cap=cap}
cap <- paste0(
  "Things."
)
# This finds lambda values at the optimised weighting parameter settings.
data <- .get_transformation_parameters_two_sided(manuscript_dir = manuscript_dir)

>>>>

Power transformations aim to transform features to a normal distribution. However, this may not always be successful or possible. Deviations from normality can be detected by normality tests, such as the Shapiro-Wilk test [@Shapiro1965-zd]. In practice, normality tests may be too stringent to assess goodness of fit in presence of large sample sizes, outliers or a combination of the two. Here we develop an empirical test for central normality.

Let central normality be defined as normality of central $\kappa$ portion of the data, i.e. $\mathbf{X}_{\text{central}} = \left\{x_i \in \mathbf{X} \, | \,  \frac{1-\kappa}{2} \leq  p_i \leq \frac{1 + \kappa}{2}\right\}$, with $p_i$ probabilities of the empirical distribution, as previously.
We then compute the residual errors between the z-scores of the transformed feature $\phi^{\lambda, x_0} (\mathbf{X})$ and the expected z-scores from a standard normal distribution: $r_i =\left| \left( \phi^{\lambda, x_0}(x_i) - \mu_M)\right) / \sigma_M - F^{-1}_{\mathcal{N}}(p_i) \right|$, with $\mu_M$ and $\sigma_M$ are robust Huber M-estimates of location and scale of the transformed feature $\phi^{\lambda, x_0} (\mathbf{X})$ [@Huber1981-su].
The set of residual errors for the central portion of the data is then $\mathbf{R}_{\text{central}} = \left\{ r_i \in \left\{ r_1, r_2, \ldots, r_n\right\} \, | \,  \frac{1-\kappa}{2} \leq  p_i \leq \frac{1 + \kappa}{2}\right\}$.

To be continued.

@@

```{r optimal_weighting_function_all_criteria_box_cox, warning=FALSE, message=FALSE, fig.cap=cap}
cap <- paste0(
  "Things."
)
# This finds lambda values at the optimised weighting parameter settings.
data <- .get_transformation_parameters(manuscript_dir = manuscript_dir)

@@

```{r optimal_weighting_function_all_criteria_yeo_johnson, warning=FALSE, message=FALSE, fig.cap=cap}
cap <- paste0(
  "Things."
)
# This finds lambda values at the optimised weighting parameter settings.
data <- .get_transformation_parameters(manuscript_dir = manuscript_dir)
